---
title: "Survey Reweighting"
output: html_notebook
---

This notebook contains code to reproduce the survey response analyses found in the paper "Don't Let Me Be Misunderstood: Comparing Intentions and Perceptions in Online Conversations" (WWW '20) by Jonathan P. Chang, Justin Cheng, and Cristian Danescu-Niculescu-Mizil.

In this R notebook, we show how survey B (perceptions) was reweighted using post-stratification to match the population distribution of survey A (intentions).

Notebook author: Justin Cheng (jcheng@fb.com)

Additional thanks: Ryan S. Ritter for the original reweighting code

Copyright (c) Facebook, Inc. and its affiliates.

This source code is licensed under the MIT license found in the
LICENSE file in the root directory of this source tree.

```{r setup}
knitr::opts_chunk$set(echo = T)
knitr::opts_chunk$set(fig.width=8, fig.height=4.94)
library(tidyverse)
library(ggthemes)
library(survey)
```

### Define functions for re-weighting

```{r}
# Define population strata
get_pop_groups <- function(pop_data) {
  pop_groups <- pop_data %>%
    filter(gender %in% c("1", "2") & !is.na(age)) %>%
    mutate(
      age_strata = ifelse(age <= 17, "13_17",
                   ifelse(age <= 24, "18_24",
                   ifelse(age <= 44, "25_44",
                   ifelse(age <= 64, "45_64", "65_plus")))),
      overall_strata = paste(gender, age_strata, sep="_")
    ) %>%
    group_by(overall_strata) %>%
    summarise(
      n = n()
    ) %>%
    ungroup() %>%
    mutate(
      total = sum(as.numeric(n)),
      proportion = n / total
    ) %>%
    dplyr::select(
      overall_strata,
      proportion
    )
  return(pop_groups)
}

# Define survey strata
get_df_with_groups <- function(df) {
  df_with_groups <- df %>%
    filter(gender %in% c("1", "2") & !is.na(age)) %>%
    mutate(
      age_strata = ifelse(age <= 17, "13_17",
                   ifelse(age <= 24, "18_24",
                   ifelse(age <= 44, "25_44",
                   ifelse(age <= 64, "45_64", "65_plus")))),
      overall_strata = paste(gender, age_strata, sep="_")
    ) %>%
    dplyr::select(
      info_seeking,
      info_giving,
      opinion_seeking,
      opinion_giving,
      joking,
      overall_strata
    ) %>%
    na.omit()
  return(df_with_groups)
}

# Make sure that all strata in the survey data are in the population sample
check_strata <- function(pop_groups, df_with_groups) {
  print(paste("# Strata for Sample:", length(table(df_with_groups$overall_strata)), " / # for Population Data:", length(table(pop_groups$overall_strata))))

  stopifnot(length(names(table(df_with_groups$overall_strata))[!names(table(df_with_groups$overall_strata)) %in% names(table(pop_groups$overall_strata))]) == 0)
}

# Plot actual vs. expected distribution
plot_group_comparison <- function(pop_groups, df_with_groups, text_size) {
  actual <- as.data.frame(
    prop.table(
      table(df_with_groups$overall_strata)
    )
  ) %>%
    dplyr::select(
      overall_strata = Var1,
      proportion = Freq
    ) %>%
    mutate(
      distribution = "actual"
    )

  expected <- pop_groups %>%
    dplyr::select(
      overall_strata,
      proportion
    ) %>%
    mutate(
      distribution = "expected"
    )

  comparison <- rbind(actual, expected)

  comparison %>%
    ggplot(aes(x = overall_strata, y = proportion, fill = distribution)) +
    geom_bar(stat = "identity", position=position_dodge(.5)) +
    labs(title = "Actual vs. Expected Distribution", x=NULL, y="Proportion") +
    theme_few() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size=text_size))
}

# Reweight sample based on population using post-stratification
get_stratification <- function(pop_groups, df_with_groups) {
  # Create population frequencies
  n.sample <- df_with_groups %>% summarise(n.sample = n())
  pop_strata <- merge(pop_groups, n.sample) %>%
    mutate(
      # Make sure that Frequency is at least 1 if proportion is > 0
      Freq = ifelse(proportion > 0, pmax(round(proportion * n.sample, 0), 1), 0)
      # Freq = ceiling(proportion * n.sample)
    ) %>%
    dplyr::select(overall_strata, Freq)

  has_partial <- length(table(df_with_groups$overall_strata)) != length(table(pop_groups$overall_strata))

  # Stratify
  df_with_groups.unweighted <- svydesign(ids = ~1, data = df_with_groups)
  df_with_groups.post.stratified <- postStratify(
    design = df_with_groups.unweighted,  # this is our unweighted survey design object
    strata = ~overall_strata, # variable in sample to weight on
    population = pop_strata, # variable in population use to reweight sample
    partial = has_partial # set this to FALSE to enforce that no empty strata exist
  )

  # Check weights and trim
  wts <- weights(df_with_groups.post.stratified)
  wts_before <- data.frame(
    category = "Before Trimming",
    min = min(wts),
    q1 = quantile(wts, 0.25),
    med = quantile(wts, 0.5),
    mean = mean(wts),
    q3 = quantile(wts, 0.75),
    max = max(wts)
  )
  
  df_with_groups.post.stratified <- trimWeights(df_with_groups.post.stratified, lower=0.3, upper=5, strict = TRUE)
  wts <- weights(df_with_groups.post.stratified)
  wts_after <- data.frame(
    category = "After Trimming",
    min = min(wts),
    q1 = quantile(wts, 0.25),
    med = quantile(wts, 0.5),
    mean = mean(wts),
    q3 = quantile(wts, 0.75),
    max = max(wts)
  )
  wts_all <- rbind(wts_before, wts_after)
  rownames(wts_all) <- NULL
  print(wts_all)

  return(df_with_groups.post.stratified)
}
```

### Reweight survey B based on the population distribution in survey A

```{r}
df1 <- read.table("survey_a_responses_cached_notext.tsv", sep = "\t", header=T)
df2 <- read.table("survey_b_responses_cached_notext.tsv", sep = "\t", header=T)
pop_groups <- get_pop_groups(df1)
df_groups <- get_df_with_groups(df2)
check_strata(pop_groups, df_groups)
plot_group_comparison(pop_groups, df_groups, 12)
df_groups.post.stratified <- get_stratification(pop_groups, df_groups)
```

### Recover reweighted distribution

```{r}
all_weights <- c()

for (goal in c("joking", "info_giving", "info_seeking", "opinion_giving", "opinion_seeking")) {
  # Use svyquantile to recover the reweighted distribution for plotting (and comparison)
  # Change the below to seq(0,1,.001) and table(x$quantiles) / 1000 for increased precision
  x <- svyquantile(as.formula(paste0("~", goal)), design=df_groups.post.stratified, seq(0,1,.005), ci=TRUE)
  y_df2 <- table(x$quantiles) / 200
  y_df1 <- table(df1[,goal]) / sum(!is.na(df1[,goal]))
  
  all_weights <- rbind(
    all_weights,
    data.frame(y_df2) %>%
      mutate(category = "perception", goal = goal),
    data.frame(y_df1) %>%
      mutate(category = "intention", goal = goal)
  )
}
```

### Plot distribution of reweighted survey responses

```{r}
all_weights %>%
  ggplot(aes(x = Var1, y = Freq, group = category, fill = category)) +
  facet_grid(. ~ goal) +
  geom_bar(stat = "identity", position = "dodge")
```

### Get means for each goal for each survey

```{r}
all_weights %>%
  group_by(category, goal) %>%
  summarise(
    avg = round(sum(as.numeric(Var1) * Freq), 2)
  )
```

### Write results to file

```{r}
# write.table(all_weights, file = "survey_a_b_reweighted.tsv", sep = "\t", quote=F, row.names = F)
```
